---
title: "Add mock data"
output: github_document
---
## Setup the environment

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("~/Documents/Work/Inoventik - local/RStudio/KYC-Use-Case-RStudio")
library(readr)
```

### KYC Analysis proper

## Load data

First, we need to locate the data provided for analysis.

```{r}
input_loc <- "./inputs/"
credit_file <- "credit_test.csv"
```

Now, let's load and look at the credit list:
```{r}
credit <- read.csv(paste0(input_loc, credit_file))
str(credit)

```

## Prepare test data

Let's extract the relevant columns, and see what the initial structure, values, and summary looks like. In this case, the pertinent columns are "Customer.Name" and "Date.of.Birth"

```{r}
credit <- credit[,c("Customer.Name","Date.of.Birth")]
head(credit, 10)
summary(credit)
str(credit)
```

Now let's load the mock data

```{r}
file_loc <- "inputs/sample data raw/"
mock_data <- read_csv(paste0(file_loc,"MOCK_DATA_10k_r.csv"))
summary(mock_data)

```

Now let's combine the name fields into a full name field

```{r}
mock_data$fullname <- paste0(mock_data$last_name,", ",mock_data$first_name)
str(mock_data$fullname)
```

Let's put the mock data into our credit file

```{r}
credit$Customer.Name <- mock_data$fullname
credit$Date.of.Birth <- mock_data$birth_date
head(credit)
summary(credit)
str(credit)
```


